### 2025-11-19 getting-started.qmd
20251118 - commonality analysis

   install.packages(c(
     "petersenlab","remotes","knitr","rmarkdown","tidyverse","nflverse",
     "tidymodels","easystats","broom","broom.mixed","psych","downlit","xml2",
     "gsisdecoder","progressr","DescTools","pwr","pwrss","WebPower","XICOR",
     "dagitty","ggdag","ggtext","gghighlight","ggExtra","patchwork","pROC",
     "lme4","lmerTest","MuMIn","emmeans","pbkrtest","sjstats","AICcmodavg",
     "rstan","brms","tidybayes","bbmle","fitdistrplus","sn","mclust","magrittr",
     "viridis","viridisLite","msir","plotly","webshot2","quantmod","fPortfolio",
     "NMOF","nFactors","xts","zoo","forecast","parallelly","doParallel",
     "missRanger","ggridges","powerjoin","bestNormalize","LongituRF","gpboost",
     "mgcv","rms","car","lavaan","lavaanPlot","lavaangui","mice","miceadds",
     "interactions","robustbase","ordinal","MASS","data.table","future",
     "future.apply","SimDesign","domir","GGally","Rglpk","TTR"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

>>>>

   install.packages(c(
     "petersenlab","remotes","knitr","rmarkdown","tidyverse","nflverse",
     "tidymodels","easystats","broom","broom.mixed","psych","downlit","xml2",
     "gsisdecoder","progressr","DescTools","pwr","pwrss","WebPower","XICOR",
     "dagitty","ggdag","ggtext","gghighlight","ggExtra","patchwork","pROC",
     "lme4","lmerTest","MuMIn","emmeans","pbkrtest","sjstats","AICcmodavg",
     "rstan","brms","tidybayes","bbmle","fitdistrplus","sn","mclust","magrittr",
     "viridis","viridisLite","msir","plotly","webshot2","quantmod","fPortfolio",
     "NMOF","nFactors","xts","zoo","forecast","parallelly","doParallel",
     "missRanger","ggridges","powerjoin","bestNormalize","LongituRF","gpboost",
     "mgcv","rms","car","lavaan","lavaanPlot","lavaangui","mice","miceadds",
     "interactions","robustbase","ordinal","MASS","data.table","future",
     "future.apply","SimDesign","domir","GGally","Rglpk","TTR","rockchalk",
     "yhat"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

### 2025-11-19 index.qmd
20251118 - commonality analysis

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "broom", "broom.mixed", "psych", "downlit", "xml2", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "ggtext", "gghighlight", "ggExtra", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", "fitdistrplus", "sn", 
  "mclust", "magrittr", "viridis", "viridisLite", "msir", "plotly", "webshot2", 
  "quantmod", "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast",
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "bestNormalize", "LongituRF", "gpboost", "cmdstanr", "mgcv", "rms", "car", 
  "lavaan", "lavaanPlot", "mice", "miceadds", "interactions", "robustbase", 
  "ordinal", "MASS", "data.table", "future", "future.apply", "SimDesign", 
  "domir", "GGally","Rglpk","TTR",
  "base","graphics","grDevices","grid","utils", # packages that are included with base R; get the full list with: rownames(installed.packages(priority="base"))
  "tidyverse", "ggplot2", "dplyr", "lubridate", # packages that are part of the tidyverse ecosystem
  "nflverse", "nflfastR", "nflseedR", "nfl4th", "nflreadr", "nflplotR", # packages that are part of the nflverse ecosystem
  "tidymodels", "rsample", "parsnip", "recipes", "tune", "yardstick", # packages that are part of the tidymodels ecosysyem
  "easystats", "see", "performance", "parameters", "correlation", "effectsize", # packages that are part of the easystats ecosystem
  "learnr", "remotes", "shiny", "PearsonDS", "lavaangui", "dynamic", "r4ds.tutorials" # packages that are cited but not used for computation (and thus do not need to be installed by me or readers)
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "broom", "broom.mixed", "psych", "downlit", "xml2", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "ggtext", "gghighlight", "ggExtra", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", "fitdistrplus", "sn", 
  "mclust", "magrittr", "viridis", "viridisLite", "msir", "plotly", "webshot2", 
  "quantmod", "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast",
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "bestNormalize", "LongituRF", "gpboost", "cmdstanr", "mgcv", "rms", "car", 
  "lavaan", "lavaanPlot", "mice", "miceadds", "interactions", "robustbase", 
  "ordinal", "MASS", "data.table", "future", "future.apply", "SimDesign", 
  "domir", "GGally","Rglpk","TTR","rockchalk","yhat",
  "base","graphics","grDevices","grid","utils", # packages that are included with base R; get the full list with: rownames(installed.packages(priority="base"))
  "tidyverse", "ggplot2", "dplyr", "lubridate", # packages that are part of the tidyverse ecosystem
  "nflverse", "nflfastR", "nflseedR", "nfl4th", "nflreadr", "nflplotR", # packages that are part of the nflverse ecosystem
  "tidymodels", "rsample", "parsnip", "recipes", "tune", "yardstick", # packages that are part of the tidymodels ecosysyem
  "easystats", "see", "performance", "parameters", "correlation", "effectsize", # packages that are part of the easystats ecosystem
  "learnr", "remotes", "shiny", "PearsonDS", "lavaangui", "dynamic", "r4ds.tutorials" # packages that are cited but not used for computation (and thus do not need to be installed by me or readers)
)

### 2025-11-19 multiple-regression.qmd
20251118 - commonality analysis

```{r}
library("petersenlab")
library("rms")
library("car")
library("bestNormalize")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("parallelly")
library("robustbase")
library("ordinal")
library("MASS")
library("broom")
library("rockchalk")
library("effectsize")
library("tidymodels")
library("tidyverse")
library("knitr")
```

@@

@@

>>>>

```{r}
library("petersenlab")
library("rms")
library("car")
library("bestNormalize")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("parallelly")
library("robustbase")
library("ordinal")
library("MASS")
library("broom")
library("rockchalk")
library("effectsize")
library("yhat")
library("tidymodels")
library("tidyverse")
library("knitr")
```

@@

### Commonality Analysis {#sec-multipleRegressionCommonalityAnalysis}

Commonality analysis decomposes the model's $R^2$ into coefficients that represent the proportion of variance accounted for uniquely by each [predictor variable](#sec-correlationalStudy) and the proportion of variance accounted for that is shared in each possible combination of the [predictor variables](#sec-correlationalStudy).
Below we conduct a commonality analysis using the `yhat::calc.yhat()`, `yhat::commonality()`, and `yhat::commonalityCoefficients()` functions of the `yhat` package [@R-yhat].

```{r}
yhat::calc.yhat(linearRegressionModel)

apsOut <- yhat::aps(
  dataMatrix = player_stats_seasonal %>% 
    filter(position %in% c("WR")) %>% 
    select(fantasyPoints, age, height, weight, target_share),
  dv = "fantasyPoints",
  ivlist = list("age", "height", "weight", "target_share"))

yhat::commonality(apsOut)

commonalityAnalysis <- yhat::commonalityCoefficients(
  dataMatrix = player_stats_seasonal %>% 
    filter(position %in% c("WR")) %>% 
    select(fantasyPoints, age, height, weight, target_share),
  dv = "fantasyPoints",
  ivlist = list("age", "height", "weight", "target_share"))

commonalityAnalysis
```

@@

We can also conduct a dominance analysis using the `yhat::dominance()` function of the `yhat` package [@R-yhat].

```{r}
yhat::dominance(apsOut)
```
